Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-24 manuscript/draft.Rmd
no ref needed here.
This is explained further in the 6th discussion paragraph

These results raise a number of important issues. First, we should be skeptical
of predictions about future biodiversity from models that have not been
validated in terms of repeated observations at the same site. Since site-level
richness is relatively stable [[refs]], model evaluations that show high
accuracy across spatial gradients may not indicate much about a model's ability
to predict changes over time. This issue has also recently been highlighted as a
potential downside of using SDMs to predict the future locations of individual
species [@rapacciuolo2012; @oedekoven2017]. This result is particularly sobering
because SDMs form the main foundation for estimates of the predicted loss of
biodiversity to climate change [@thomas2004; @thuiller2011; @urban2015].

>>>>

These results raise a number of important issues. First, we should be skeptical
of predictions about future biodiversity from models that have not been
validated in terms of repeated observations at the same site. Since site-level
richness is relatively stable, model evaluations that show high
accuracy across spatial gradients may not indicate much about a model's ability
to predict changes over time. This issue has also recently been highlighted as a
potential downside of using SDMs to predict the future locations of individual
species [@rapacciuolo2012; @oedekoven2017]. This result is particularly sobering
because SDMs form the main foundation for estimates of the predicted loss of
biodiversity to climate change [@thomas2004; @thuiller2011; @urban2015].
